### 2018-10-09 paper/finitecomplete-failures.tex
Fixed typos in proof of Lemma 6.

% -------------------------------------------------------------------------
\begin{theorem}\label{th:failurestest}
Let $P$ be a non-terminating, divergence-free CSP process over alphabet $\Sigma$ whose
normalised transition graph $G(P)$ has $p$ states. Define fault domain ${\cal
D}$ as the set of all divergence-free CSP processes over alphabet $\Sigma$,
whose transition graph has at most $q$ states with $q \ge p$. Then the test
suite
\[
\TS_F = \{ U_F(j)~|~0 \le j < pq  \}\quad\text{$U_F(j)$ specified in (\ref{eq:UFP})}
\]
is complete with respect to ${\cal F} = (P,\lessdet_F,{\cal D})$.
\end{theorem}
% ------------------------------------------------------------------------
%
The proof of the theorem follows from the two lemmas below. The first states
that test suite $\TS_F$ is sound, the second states that the suite is also
exhaustive.
%
\begin{lemma}\label{lemma:mainfsound}
A test suite $\TS_F$ generated from a CSP process $P$, as specified in
Theorem~\ref{th:failurestest}, is passed by every CSP process $Q$ satisfying
$P\lessdet_F Q$.
\end{lemma}
\begin{proof}{~}We make two points in separate steps below. The
first is that the test execution cannot reach branch~(\ref{eq:ufa}) and raise
a $fail$ event.  The second is that it cannot deadlock without raising a
$pass$ event. This case would also be interpreted as FAIL, since then
$\epass\then\Stop$ is not failures refined by $(Q\parallel[\Sigma]
U_F(j))\hide \Sigma$.
% alcc: part of the explanation above was in the following lemma, but it is already
% relevant here.

@@

\paragraph{Step~2.1} Suppose that the test execution blocks at branch (\ref{eq:ufc})
after having run through trace $s$ with $\#s < j$. 
Since  $P\lessdet_T Q$ by assumption, $s$ is a trace of $P$, thus 
$U_F(j)/s = U_F(j,\#s,G(P)/s)$ according to Lemma~\ref{lemma:ufproperties}. Therefore,
$U_F(j)/s$  can enter  branch (\ref{eq:ufc}) with any event from $[G(P)/s]^0$.
Since we assume that $(Q\parallel[\Sigma] U_F(j))/s$ deadlocks, this means that
$[G(P)/s]^0$ is {\it not} a hitting set of $\minhits(Q/s)$, because otherwise at least
on $e\in [G(P)/s]^0$ would be accepted by $Q/s$. Now suppose that $\minhits(G(P)/s) = \varnothing$. Then   branch (\ref{eq:ufb}) can be entered, and the test 
stops after $\epass$. Otherwise, if $\minhits(G(P)/s) \neq \varnothing$, let
$H\in\minhits(G(P)/s)$. Since $H$ only contains elements that are contained in some minimal acceptance of $P/s$, and all these minimal acceptances are subsets of 
$[G(P)/s]^0$, $H$ is a subset of $[G(P)/s]^0$ as well. Since $[G(P)/s]^0$, however, 
is not an element of $\minhits(Q/s)$, also $H$ is not contained in $\minhits(Q/s)$.
Now this is a contradiction to Lemma~\ref{lemma:hseta}, since $Q\ conf\ P$ by assumption,
so $H$ should also be a (not necessarily minimal) hitting set in $\minhits(Q/s)$.
This proves that the test execution cannot block  at branch (\ref{eq:ufc})
without being able to pass the test by entering branch (\ref{eq:ufb}).

>>>>

% -------------------------------------------------------------------------
\begin{theorem}\label{th:failurestest}
Let $P$ be a non-terminating, divergence-free CSP process over alphabet $\Sigma$ whose
normalised transition graph $G(P)$ has $p$ states. Define fault domain ${\cal
D}$ as the set of all divergence-free CSP processes over alphabet $\Sigma$,
whose transition graph has at most $q$ states with $q \ge p$. Then the test
suite
\[
\TS_F = \{ U_F(j)~|~0 \le j < pq  \}\quad\text{$U_F(j)$ specified in (\ref{eq:UFP})}
\]
is complete with respect to ${\cal F} = (P,\lessdet_F,{\cal D})$.
\end{theorem}
% ------------------------------------------------------------------------
%
The proof of the theorem follows from the two lemmas below. The first states
that test suite $\TS_F$ is sound, the second states that the suite is also
exhaustive.
%
\begin{lemma}\label{lemma:mainfsound}
A test suite $\TS_F$ generated from a CSP process $P$, as specified in
Theorem~\ref{th:failurestest}, is passed by every CSP process $Q$ satisfying
$P\lessdet_F Q$.
\end{lemma}
\begin{proof}{~}We make two points in separate steps below. The
first is that the test execution cannot reach branch~(\ref{eq:ufa}) and raise
a $fail$ event.  The second is that it cannot deadlock without raising a
$pass$ event. This case would also be interpreted as FAIL, since then
$\epass\then\Stop$ is not failures refined by $(Q\parallel[\Sigma]
U_F(j))\hide \Sigma$.

@@

\paragraph{Step~2.1} Suppose that the test execution blocks at branch (\ref{eq:ufc})
after having run through trace $s$ with $\#s < j$. 
Since  $P\lessdet_T Q$ by assumption, $s$ is a trace of $P$, thus 
$U_F(j)/s = U_F(j,\#s,G(P)/s)$ according to Lemma~\ref{lemma:ufproperties}. Therefore,
$U_F(j)/s$  can enter  branch (\ref{eq:ufc}) with any event from $[G(P)/s]^0$.
Since we assume that $(Q\parallel[\Sigma] U_F(j))/s$ deadlocks, this means that
$[G(P)/s]^0$ is {\it not} a hitting set of $\minaccs(Q/s)$, because otherwise at least
on $e\in [G(P)/s]^0$ would be accepted by $Q/s$. Now suppose that $\minhits(G(P)/s) = \varnothing$. Then   branch (\ref{eq:ufb}) can be entered, and the test 
stops after $\epass$. Otherwise, if $\minhits(G(P)/s) \neq \varnothing$, let
$H\in\minhits(G(P)/s)$. Since $H$ only contains elements that are contained in some minimal acceptance of $P/s$, and all these minimal acceptances are subsets of 
$[G(P)/s]^0$, $H$ is a subset of $[G(P)/s]^0$ as well. Since $[G(P)/s]^0$, however, 
is not a hitting set of $\minaccs(Q/s)$, also $H$ is not a hitting set of 
$\minaccs(Q/s)$.
Now this is a contradiction to Lemma~\ref{lemma:hseta}, since $Q\ conf\ P$ by assumption,
so $H$ should also be a (not necessarily minimal) hitting set in $\minaccs(Q/s)$.
This proves that the test execution cannot block  at branch (\ref{eq:ufc})
without being able to pass the test by entering branch (\ref{eq:ufb}).
